Storm Surges

### 2014-07-21 RoughWork/manuscript.tex
Included surge timing/amplitude infor for Dec 2006

\subsection{Spatial Extent of Surge: Dec 15, 2006}
On Dec 15, 2006, a major storm with wind gusts over 120 km/hr caused significant damage to many coastal communities on the Pacific Northwest. In British Columbia, over 250,000 residents were left without power due to downed trees and hydro lines. Although the storm was very strong and the observed residual at Point Atkinson reached 85 cm, this event did not coincide with high tide and so no siginificant flooding occurred in the Vancouver area\citep{forseth2006adaptation}. This event has been used to examine the propgation of the surge throughout the domain. First, an assessment of the accuracy of the hindcast is provided.

>>>>

\subsection{Spatial Extent of Surge: Dec 15, 2006}
On Dec 15, 2006, a major storm with wind gusts over 120 km/hr caused significant damage to many coastal communities on the Pacific Northwest. Although the storm was very strong and the observed residual at Point Atkinson reached 84 cm, this event did not coincide with high tide and so no siginificant or reported flooding occurred in the Vancouver area\citep{forseth2006adaptation}. This event has been used to examine the propgation of the surge throughout the domain. First, an assessment of the accuracy of the hindcast is provided.

Point Atkinson observed a maximum surge amplitude of 84 cm, which is approximately 20 cm higer than the model result, however the timing of the surge agrees almost exactly. The best agreement occurs at Victoria where the observed surge was 62 cm and the model returned 54 cm. At all of the locations, the model predicted the maximum surge to occur within 3.5 hours of the observed surge. Typically, the modelled surge was too early, in contrast to the later predictions in the Feb, 4 2006 case. Errors in the modelled water level at the timing of maximum surge were of the same order as the errors in the surge amplitude.
